ManuscriptGAM

### 2024-03-06 Code/Plots_GAM.Rmd

```{r load libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
library(plotly)
library(mgcv)
library(tidymv)
library(CCA)
library(vegan)
library(cowplot)
library(glue)
library(gtable)
library(car)
library(MASS) # estimating linear models through generalized least squares (GLS), fitting negative binomial linear models, the robust fitting of linear models, and Kruskal's non-metric multidimensional scaling.
library(faraway) # LM package
library(gridExtra)
library(ggh4x)
library(ggspectra) 
library(photobiologyWavebands) 
# library(photobiology)
library(metR)
library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.

@@

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
 limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend1 <- g_legend(g_dummy1)
(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend2 <- g_legend(g_dummy2)
(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend3 <- g_legend(g_dummy3)

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5),
                     c(1, 1, 1, 1, 4), 
                     c(1, 1, 1, 1, 4)
                     )

@@

p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)

@@

# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
``` {r GAM Plot Blue WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

@@

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  C.   " ~ .(GamStrain) ~ '    2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  B.   " ~ .(GamStrain) ~ '    25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("  A.   " ~ .(GamStrain) ~ '    250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5),
                     c(1, 1, 1, 1, 4), 
                     c(1, 1, 1, 1, 4)
                     )

@@

p3 <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(FP1, "Plots", sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 10, width = 6)

# for presentation
  ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3,  height = 7.6, width = 6)

@@

``` {r GAM PUR comparison}

GamWL = c("deltaOD") #deltaOD OD720
Proxy= "[~Chl]" #~Chl ~Cells 
GamParaMod = "Lmu"
#GamVar = c("450")# 450 660 WW
GamStrain = "MED4" # MIT9313 MED4 SS120
# ErrorTol = 20
OxyLev = 250

################ check smooth terms #https://fromthebottomoftheheap.net/2017/12/14/difference-splines-ii/
#https://stackoverflow.com/questions/70922283/gam-smooths-interaction-differences-calculate-p-value-using-mgcv-and-gratia-0
PurGAM <- ComGrowthFits %>%
  mutate(ordPP = ordered(Photoperiod, levels = c('4', '8', '12', '16')),
         Lmu_seFlag = case_when(se/estimate*100 < ErrorTolGrowth ~ 1, #filters faulty data where Standarderror larger +/- Errortolerance
                         FALSE ~ 0)) %>%
  ungroup() %>%
  dplyr::filter(
                Photoperiod != 4, 
                Lmu_seFlag == 1,
                term %in% GamParaMod,
                Wavelength %in% GamWL,
                Strain %in% GamStrain,
                O2_uM %in% OxyLev) %>%
  mutate(estimate = estimate*24,
         se = se*24)

m_PUR_gam <- gamm(estimate ~ s(PURPhotonDose_day, k = -1) + s(PURPhotonDose_day, by = ordPP), random=list(WL=~1), data = PurGAM, method = "REML")
m_PUR_gam <- m_PUR_gam$gam

plot(m_PUR_gam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
summary(m_PUR_gam)

# zoom_Chl_TreatCheck <- zoom_log %>%
#   filter(Group != "ES") %>%
#   mutate(ordGroup = ordered(Group, levels = c('ES', 'Fish', 'noFish')))
# 
# m_Chl_Treatgam <- gamm(Chla_ugL ~ Group +  s(DayFrFrst) +s(DayFrFrst, by = ordGroup), random=list(SampleYear=~1), data = zoom_Chl_TreatCheck, method = "REML")
# m_Chl_Treatgam <- m_Chl_Treatgam$gam
# 
# plot(m_Chl_Treatgam, shade = TRUE, pages = 1, scale = 0, seWithMean = TRUE)
# summary(m_Chl_Treatgam)

# PurGAM <- ComGrowthFits %>% 
#   ungroup() %>%
#   dplyr::filter(Lmu_seFlag == 1, 
#                 term %in% GamParaMod, 
#                 Wavelength %in% GamWL,
#                 strain %in% GamStrain) %>%
#   mutate(estimate = estimate*24,
#          se = se*24) %>%
#   group_by(Strain, Wavelength, O2_uM, Photoperiod) %>%
#   nest() %>%
#   dplyr::arrange(Strain, Wavelength, O2_uM) %>%
#   mutate(GamModel = map(data, ~possibGAM(estimate ~ s(PUR_day, k = 3) + s(Photoperiod, k = 3) + ti(Photoperiod, Par_ue, k = 3),  data = .x,
#                                     family = "gaussian"(link = "log"), 
#                                     method = "REML")),
#          predicted = map(GamModel, ~possibPRED(.x, newdata = PAR_Photoperiod_Model_predi, type = 'response', se.fit=TRUE)),
#          augmented = map(GamModel, ~augment(.x))
#          )
# 
# PicoGAM_Pred <- PicoGAM %>%
#   dplyr::select(Strain, Wavelength, WL, O2_uM, predicted) %>%
#   dplyr::filter(predicted != "NULL") %>%
#   rowwise() %>%
#   mutate(db = list(cbind(predicted, PAR_Photoperiod_Model_predi))) %>%
#   dplyr::select(-predicted) %>%
#   unnest(col = db) %>%
#   group_by(Strain, Wavelength, WL, O2_uM) %>%
#   dplyr::filter(fit < 1) %>% #with two expections, growth rates were never higher than 0.06; GAM model creates some unrealistic high growth rates due to low data availability
#   mutate(
#     fit = case_when(se.fit/fit*100 < ErrorTol ~ fit*1, #filters faulty data where Standarderror larger +/- Errortolerance
#                          FALSE ~ fit)
#   # ,fit = case_when(fit >= quantile(fit, 0.75, na.rm = TRUE) ~ fit*1, #leaves only top-10%, that means fastest growth rates in the dataframe
#   #                 FALSE ~ fit)
#   )

@@

>>>>

```{r load libraries, message=FALSE}
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)
library(minpack.lm)
library(nlstools)
library(nlsMicrobio)
library(plotly)
library(mgcv)
library(tidymv)
library(CCA)
library(vegan)
library(cowplot)
library(glue)
library(gtable)
library(car)
library(MASS) # estimating linear models through generalized least squares (GLS), fitting negative binomial linear models, the robust fitting of linear models, and Kruskal's non-metric multidimensional scaling.
library(faraway) # LM package
library(grid)
library(gridExtra)
library(ggh4x)
library(ggspectra) 
library(photobiologyWavebands) 
# library(photobiology)
library(metR)
library(Rcpp) #'Rcpp' package provides R functions as well as C++ classes which offer a seamless integration of R and C++.

@@

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

@@

(g_dummy1 <- ggplot(subset(HyperChlPlotLow, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend1 <- g_legend(g_dummy1)
(g_dummy2 <- ggplot(subset(HyperChlPlotInt, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend2 <- g_legend(g_dummy2)
(g_dummy3 <- ggplot(subset(HyperChlPlotHigh, Color_name == w_length2rgb(WL_nm)), aes(Photoperiod, Par_ue, fill=fit)) + geom_tile()
+ scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", w_length2rgb(WL_nm)),
  limits  = range(minMu, 1.0), na.value = "white") + theme_classic())
legend3 <- g_legend(g_dummy3)

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5)
                     ,
                     c(1, 1, 1, 1, 4),
                     c(1, 1, 1, 1, 4)
                     )

@@

p3_Red <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)

@@

# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot for each strain
``` {r GAM Plot Blue WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

@@

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
      # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35),
          axis.text.y = element_blank(),
          axis.line.y = element_blank(),
          axis.ticks.y = element_blank()))

@@

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23),
          axis.text.y = element_blank(),
          axis.line.y = element_blank(),
          axis.ticks.y = element_blank()))

@@

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
    # ylab("                                  ") +
      ylab(NULL)+
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=20),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35),
          axis.text.y = element_blank(),
          axis.line.y = element_blank(),
          axis.ticks.y = element_blank()))

@@

LayoutNiche <- rbind(
                     c(3, 3, 3, 3, 6),
                     c(3, 3, 3, 3, 6),
                     c(2, 2, 2, 2, 5),
                     c(2, 2, 2, 2, 5)
                     ,
                     c(1, 1, 1, 1, 4),
                     c(1, 1, 1, 1, 4)
                     )

@@

p3_Blue <- grid.arrange(ContourLowO2 + theme(legend.position = 'none'), ContourIntO2 + theme(legend.position = 'none'), ContourHighO2 + theme(legend.position = 'none'), legend1, legend2, legend3, layout_matrix = LayoutNiche)

@@

#  for thesis
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 10, width = 6)

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Blue,  height = 7.6, width = 6)

@@

```{r combine red and blue light GAM plots}

CombinedGAM <- plot_grid(p3_Red, p3_Blue)

x.grob <- textGrob("Photoperiod (h)", 
                   gp = gpar(fontface="bold", fontsize = 20))

y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)

#add to plot

LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))

@@

```{r save png}
 ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)
```
